---
title: "How it works in steps"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{how_it_works}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Here we break into the parts how the imputation process is built in this package. 

```{r setup}
library(dplyr)
library(purrr)
library(tidyr)
library(syntheticpanel)
```

## Step 1. Bootstrapping

To re sample data in a reproducible way, we create bootstrapping vectors. These are then used for sub sampling input data. It all comes to a simple `sample` function form base R, which re-sample a vector of indexes with the repetitions. It is  wrapped around the two functions. 

`get_bootstrap_permutation()`

```{r}
get_bootstrap_permutation
```

`sample_vector()`

```{r}
sample_vector
```

As an example, let us create a data fame with two columns `id` and `group`. Column group is used for the group wise re-sampling and the column id is returned as an index of the new sample structure.

```{r}
sample_vector(1:10)
df <- tibble::tibble(id = 1:30, group = sort(rep(1:3, 10)))
glimpse(df)
get_bootstrap_permutation(df, 3)
```

## Step 2. Matching the nearest observation

It happens also in two steps. 

`find_one_near()` finds a nearest match of one observation from a vector of observations. 

```{r}
find_one_near
```
 
It works as:
 
```{r}
find_one_near(c("a" = 10), c(8:15), 3)
find_one_near(c("a" = 10), setNames(c(8:15), letters[1:8]), 5)
```
 
`find_near()` wraps it for matching vector with the vector. 

```{r}
find_near
```

Producing:
```{r}
obs <- setNames(rnorm(5), as.character(1:5))
match_v <- setNames(rnorm(50), as.character(1:50))
find_near(obs, match_v, n_near = 10)
```

## Step 3. Estimating matches

This is done with the `estimate_matches()` which accepts already re sampled data. Lets follow an example. We initialize the necessary data vectors X, Y, W-weights and XX1 - period 1 independent variables for predictions.

```{r}
XX <- as.matrix(mtcars[, !names(mtcars) %in% "hp"])
YY <- as.matrix(mtcars[, "hp"])
WW <- matrix(rep(1, nrow(mtcars)), ncol = 1, nrow = nrow(mtcars))
XX1 <- as.matrix(mtcars[1:10, !names(mtcars) %in% "hp"])
```

Running simple estimation and returning the output is straightforward. We run it in the full - not reduced form to see all the possible outputs of the function.

```{r}
a <- estimate_matches(x_mat = XX, y_mat = YY, w_mat = WW, x1_mat = XX1, reduced = FALSE, n_near = 5)
str(a, max.level = 1)
a$fit %>% coef()
```

Same could be done with the bootstrapping. The only difference is that we have to supply to the function a sub sampled version of data (X, Y and W).

```{r}
perm_example <- purrr::map(1:5, ~ sample(1:nrow(YY), nrow(YY), TRUE))
a_boot <-
   perm_example %>%
   purrr::map(~ syntheticpanel::estimate_matches(
     x_mat = XX[.x, ],
     y_mat = YY[.x, ],
     w_mat = WW[.x, ],
     x1_mat = XX1,
     reduced = FALSE,
     n_near = 5
   ))
```

Here is an example of the possible outcomes of the bootstrapped analysis and how they could be tackled using `purrr` package:

*    Exploring the structure:

```{r}
a_boot %>%
 str(max.level = 1)
```

*    Accessing fit of a specific bootstrap iteration

```{r}
a_boot[[3]]$fit
```

*    Doing the same with each single bootstrap iteration

```{r}
a_boot %>%
 map("fit")
```

*    Extracting coefficients from each single bootstrap iteration

```{r}
a_boot %>%
 map("fit") %>%
 map(coefficients)
```

*    Combine all coefficients in a table:

```{r}
a_boot %>%
 map("fit") %>%
 map(broom::tidy) %>%
 map(~ select(.x, term, estimate)) %>%
 map2(.y = 1:length(.), ~ rename_at(.x, vars(estimate), list(~ paste0(., "_", .y)))) %>%
 reduce(full_join)

```

The source code of the function looks like:

```{r}
estimate_matches
```

## Step 3. Wrap up around input as data frames and multiple imputations data as an output.

As a wrap-up example, we use the read me example. It is a straight forward initialization of built-in package data and running the analysis.

```{r}
glimpse(p_0_exmple)       # help(p_0_exmple)
glimpse(p_1_exmple)       # help(p_1_exmple)
glimpse(sample_bootstrap) # help(sample_bootstrap)

dep <- "price"            # Dependent variable
indep <- c("mpg", "headroom", "trunk",
           "weight", "length", "turn",
           "displacement", "gear_ratio",
           "foreign")     # independent variables
weight <- "weight"        # weight variable
extrar <- "displacement"  # any extra variable to bring from period 0 data
bt_groups <- c("psu")     # Grouping variable for bootsrapping.
                          # May be a combination of variables.
n_nearest <- 1    # numebr of the nearest observations to drow a random match
set.seed(11223344)
imputation <-
  impute_data(period_0 = p_0_exmple, 
              period_1 = p_1_exmple,
              dep_var = dep, indep_var = indep, weight_var = weight,
              group_boot_var = bt_groups,
              extra_var = extrar,
              n_boot = 5, # Numebr of bootstrap iterations
              n_near = 1)

glimpse(imputation)

# Summary of the number of observations per one ID
# 6 in total meaning that 1 observation stands for original
# non imputed data and others are bootstrap imputations
imputation %>% group_by(.id) %>% count()

# Summary of the number of observations per imputation. 7 - consisten
# 0 imputation is the original data.
imputation %>% group_by(.imp) %>% count()
```

Source code of the function is:

```{r}
impute_data
```





